\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-11 fully-abstract-comp/popl2019/paper.tex
Shorten.

\subsection{Logical relation}
\label{subsec:logical-relation}
In this section, we present the logical relation.
Unfortunately due to space considerations, we do not give a comprehensive description of it.
Instead we highlight the parts specific to the logical relation we have used and refer to the technical report~\citep{technical_report} for the details and to~\citet{skorstengaard_reasoning_2017} for a more comprehensive description of a logical relation for a capability machine.
Finally for the sake of presentation, we will sometimes omit describing details, such as step indexing, that are important for the correctness but otherwise not interesting.

>>>>

\subsection{Logical relation}
\label{subsec:logical-relation}
In this section, we present the logical relation.
Unfortunately, for space reasons, we do not give a comprehensive description of it.
Instead we highlight the parts specific to the logical relation and refer to the \citet{technical_report} for details and to~\citet{skorstengaard_reasoning_2017} for a more comprehensive description of a logical relation for a capability machine.
Finally, for presentation, we will sometimes omit details, like step indexing, that are important for correctness but otherwise not interesting.
